### 2024-11-23 scripts/05-exploratory_data_analysis.qmd
Bugs in clean_data fixed
Bugs in clean_data fixed

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  labs(title = "Total usage during different time periods from January 2017 to September 2024", 
       x = "Time interval", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") 
```
```{r, fig.width=10}

options(scipen = 999)

average_counts_start <- start %>%
  group_by(station_name) %>%
  summarize(average_count = mean(count, na.rm = TRUE))

average_counts_stop <- stop %>%
  group_by(station_name) %>%
  summarize(average_count = mean(count, na.rm = TRUE))

@@

merged_data <- merged_data %>%
  mutate(count_difference = floor(average_count.y - average_count.x))

ggplot(merged_data, aes(x = station_name, y = count_difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Four-hour average of bicycle parking and departure volumes for each station",
       x = "Station Name",
       y = "Parking volume minus departure volume")+
  ylim(-12, 3)+
  coord_flip()
```

>>>>

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  labs(title = "Total usage during different time periods from January 2017 to September 2024", 
       x = "Time interval", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") 
```
```{r, fig.width=10}
options(scipen = 999)

# Create a new column for the time interval (every 1day)
start_1day <- start %>%
  mutate(date = as.Date(time))
stop_1day <- stop %>%
  mutate(date = as.Date(time))
start_1day <- start_1day %>% select(-time)
stop_1day <- stop_1day %>% select(-time)

# Group by from(to)_station_name and the new interval, then count the occurrences
start_1day1 <- start_1day %>%
  group_by(station_name, date) %>%
  summarise(total_count = sum(count), .groups = "drop") %>%
  ungroup()
stop_1day1 <- stop_1day %>%
  group_by(station_name, date) %>%
  summarise(total_count = sum(count), .groups = "drop") %>%
  ungroup()

average_counts_start <- start_1day1 %>%
  group_by(station_name) %>%
  summarize(average_count = mean(total_count, na.rm = TRUE))

average_counts_stop <- stop_1day1 %>%
  group_by(station_name) %>%
  summarize(average_count = mean(total_count, na.rm = TRUE))

@@

merged_data <- merged_data %>%
  mutate(count_difference = ifelse((average_count.y - average_count.x) >= 0, 
                                   ceiling(average_count.y - average_count.x), 
                                   floor(average_count.y - average_count.x)))

ggplot(merged_data, aes(x = station_name, y = count_difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Difference of daily average of bicycle parking and departure volumes for each station",
       x = "Station Name",
       y = "Parking volume minus departure volume")+
  ylim(-4, 3)+
  coord_flip()
```
